Protecting Private Data in the Cloud: A Path Oblivious RAM Protocol

### 2014-11-23 paper/paper.tex
started captioning figures

\subsection{Path Oblvious RAM}
To make the Oblivious RAM system more efficient, researchers introduced Path ORAM. In this system, blocks of data are arranged into a binary tree, with a few blocks at each node of the tree. (A binary tree, pictured in {\bf Figure 2-1}, is a tree in which each node has up to two children.) Instead of accessing all blocks in order to keep a specific one secret, we can simply access all blocks along the target’s path. “Accessing” in this context means fetching a block from untrusted storage and placing it in memory to be worked on. Work on a specific block is still hidden because a group of blocks are accessed together, but the groups are much smaller, improving speed.

\begin{center}
\noindent\includegraphics[width=6cm]{220.png}
\end{center}

We summarize how Path ORAM works here. The reader can refer to \cite{PathORAM} for more details. The tree is a binary tree data structure of height $L$ and $2^L$ leaves stored on the server as a one-dimensional array. The levels are numbered 0 to $L$, where level 0 is the root, level $L$ contains the leaves (in a complete tree), and levels in between contain non-leaf nodes. Each node in the binary tree is called a bucket, and contains $z$ blocks. If a bucket contains less than $z$ “real” blocks, the remainder are composed of dummy blocks, which are indistinguishable from real blocks because buckets are stored as encrypted fixed-size arrays.

On the client side, we construct a data structure called the {\bf stash}, which stores a small subset of the data blocks, and a {\bf position map} that assigns each block to a path in the tree. Every path is uniquely defined as leading from the root to one of the $2^L$ leaf buckets. Importantly, mapping is random, allowing for multiple unrelated blocks to be mapped to one leaf. This is shown in {\bf Figure 2-1}: for example, both blocks B and E are mapped to leaf 1, and are required to reside on the path defined by this leaf (referred to as path 1). The position map is updated as blocks are accessed and their leaf assignments changed. This is critical because Path ORAM maintains the invariant that if the block is not on its assigned path, it is in the stash (if it is not, there is a bug).

>>>>

\subsection{Path Oblivious RAM}
To make the Oblivious RAM system more efficient, researchers introduced Path ORAM. In this system, blocks of data are arranged into a binary tree, with a few blocks at each node of the tree. (A binary tree, pictured in {\bf Figure \ref{fig:bintree}}, is a tree in which each node has up to two children.) Instead of accessing all blocks in order to keep a specific one secret, we can simply access all blocks along the target’s path. “Accessing” in this context means fetching a block from untrusted storage and placing it in memory to be worked on. Work on a specific block is still hidden because a group of blocks are accessed together, but the groups are much smaller, improving speed.

\begin{figure}
\begin{center}
    \includegraphics[width=6cm]{220.png}
  \caption{Example of binary tree with blocks of data}
  \label{fig:bintree}
\end{center}
\end{figure}

We summarize how Path ORAM works in {\bf Figure \ref{fig:bintree}}. The reader can refer to \cite{PathORAM} for more details. The tree is a binary tree data structure of height $L$ and $2^L$ leaves stored on the server as a one-dimensional array. The levels are numbered 0 to $L$, where level 0 is the root, level $L$ contains the leaves (in a complete tree), and levels in between contain non-leaf nodes. Each node in the binary tree is called a bucket, and contains $z$ blocks. If a bucket contains less than $z$ “real” blocks, the remainder are composed of dummy blocks, which are indistinguishable from real blocks because buckets are stored as encrypted fixed-size arrays.

On the client side, we construct a data structure called the {\bf stash}, which stores a small subset of the data blocks, and a {\bf position map} that assigns each block to a path in the tree. Every path is uniquely defined as leading from the root to one of the $2^L$ leaf buckets. Importantly, mapping is random, allowing for multiple unrelated blocks to be mapped to one leaf. This is shown in {\bf Figure \ref{fig:bintree}}: for example, both blocks B and E are mapped to leaf 1, and are required to reside on the path defined by this leaf (referred to as path 1). The position map is updated as blocks are accessed and their leaf assignments changed. This is critical because Path ORAM maintains the invariant that if the block is not on its assigned path, it is in the stash (if it is not, there is a bug).
